Checks on testing

### 2020-04-24 README.Rmd
readme
logo
draft implementation

# covid19census  <img src='inst/img/hexsticker.png' align="right" height="139" />

@@

```{r all, message=FALSE}
library(covid19census)

@@

Data regarding COVID-19 number of cases and deaths (at the county level) were obtained from the [New York Time git repository](https://github.com/nytimes/covid-19-data), whereas number of tests and hospitalizations from the [the Covid Tracking Project].

>>>>

# covid19census  <img src='inst/img/hexsticker2.png' align="right" height="139" >

@@

```{r all, message=FALSE, eval=FALSE}
library(covid19census)

@@

Data regarding COVID-19 number of cases and deaths (at the county level) were obtained from the [New York Time git repository](https://github.com/nytimes/covid-19-data), whereas number of tests and hospitalizations from the [the Covid Tracking Project](https://covidtracking.com/api}).

### 2020-04-24 inst/some_checks.Rmd
draft implementation

>>>>

```
WHO ratio positive/total to talk about reopening

```{r, message=FALSE}
t_us %>% 
  mutate(ratio_pos = positive/(positive + negative)) %>% 
  filter(date == max(date)) %>%

  ggplot(aes(reorder(state, ratio_pos), ratio_pos)) +
    geom_col() +
    scale_x_discrete(guide = guide_axis(check.overlap = TRUE, angle = 90)) +
    labs(x = NULL,
         y = "positive/(positive + negative)",
         title = "Probability of a positive test") +
    theme(legend.position = "top",
        legend.title = element_blank())
```
